Characterization of foreign direct investment in Mozambique and implications

### 2016-01-04 paper.Rmd
minor updates

#####
# PLOT
#####
cols <- colorRampPalette(brewer.pal(9, 'Blues'))(ceiling(max(temp$y2009)))
colorfy <- function(number){
  cols[round(number)]
}

>>>>

#####
# PLOT
#####
cols <- colorRampPalette(brewer.pal(9, 'Blues'))(ceiling(max(temp$y2009, na.rm = TRUE)))
colorfy <- function(number){
  cols[round(number)]
}
